Coding theory package for {\it Macaulay2}

### 2021-05-22 tex/paper.tex
progess on cover letter/ paper

\begin{example}\label{example_2.5}
 $\,$
 \begin{verbatim}
i1 : F = GF(11,Variable => a);
i2 : G = matrix table({1,2,3,4},
                      {1,a,a^2,a^3,a^4,a^5,a^6,a^7,a^8,a^9},(i,j)->j^i);
i3 : D = linearCode(G,ParityCheck => true);
i4 : D.GeneratorMatrix
o4 = | 1  -3 5  3  1 0 0 0 0 0 |
     | -3 -1 4  -4 0 1 0 0 0 0 |
     | 4  -4 -3 5  0 0 1 0 0 0 |
     | -5 -3 4  4  0 0 0 1 0 0 |
     | -4 -4 -1 3  0 0 0 0 1 0 |
     | -3 5  3  1  0 0 0 0 0 1 |
 \end{verbatim}
\end{example}

\section{Basic parameters of linear codes}~\label{pro}

The {\it dimension\/}, {\it length\/}, and {\it rate} or {\it information rate}  of a linear code are basic parameters. Given a linear code $C\subseteq \mathbb{F}^n_q$, these parameters are defined as $k=\dim_{\mathbb{F}_q} C$, $n$, and $k/n$ respectively. Another parameter of a linear code $C\subseteq \mathbb{F}^n_q$ is the {\it minimum Hamming weight}, which is given by 
\[
w_H(C)=\min\{\|c\|
\colon  c \in C, c \neq 0\},
\]
where $\| c \|$ is the number of non-zero entries of $c\in \mathbb{F}^n_q$. This parameter is important in determining the error-correcting capability of $C$; the higher the minimum Hamming weight, the more errors the code can detect and correct (see \cite{huf-pless}). This function has been implemented \textcolor{red}{Nathan, write here something about the implementation of the weight function}.

In {\it Macaulay2}, the space $\mathbb{F}_q^n$ has been called the {\it ambient module} or {\it ambient space} of $C$, while the field $\mathbb{F}_q$, the {\it alphabet} or {\it field} of $C$. As often, the elements of $C$ are referred to as {\it codewords}. The input in all the following commands implemented in the {\tt CodingTheory} package is always a linear code  {\tt C}.

@@

>>>>

\begin{example}\label{example_2.5}
 $\,$
 \begin{verbatim}
i1 : F = GF(11,Variable => a);
i2 : G = matrix table({1,2,3,4},
                      {1,a,a^2,a^3,a^4,a^5,a^6,a^7,a^8,a^9},(i,j)->j^i);
i3 : D = linearCode(G,ParityCheck => true);
i4 : D.GeneratorMatrix
o4 = | 1  -3 5  3  1 0 0 0 0 0 |
     | -3 -1 4  -4 0 1 0 0 0 0 |
     | 4  -4 -3 5  0 0 1 0 0 0 |
     | -5 -3 4  4  0 0 0 1 0 0 |
     | -4 -4 -1 3  0 0 0 0 1 0 |
     | -3 5  3  1  0 0 0 0 0 1 |
 \end{verbatim}
\end{example}
\section{Basic parameters of linear codes}~\label{pro}
The dimension $k$ and length $n$ are basic parameters of a linear code $C\subseteq \mathbb{F}^n_q$. The {\it information rate} of a linear code is defined as $k/n$. Another parameter of a linear code $C\subseteq \mathbb{F}^n_q$ is the {\it minimum distance}, which is defined as follows:
\[
w_H(C):=\min\{\|c\|
\colon  c \in C, c \neq 0\},
\]
where $\| c \|$ denotes the Hamming weight of $c\in \mathbb{F}^n_q$. This parameter is important in determining the error-correcting capability of $C$; the higher the minimum distance, the more errors the code can detect and correct (see \cite{huf-pless}). 
While the dimension and the length of linear code are computationally easy to determine, it is known that computing the minimum distance of an arbitrary linear code is an NP-hard problem \cite{Vardy}. For this task, the function {\ttfamily minimumWeight} is provided.

In {\it Macaulay2}, the space $\mathbb{F}_q^n$ has been called the {\it ambient module} or {\it ambient space} of $C$. The field $\mathbb{F}_q$ is called the {\it alphabet} or {\it field} of $C$. As often, the elements of $C$ are referred to as {\it codewords}. The input in all the following commands implemented in the {\tt CodingTheory} package is always a linear code  {\tt C}:

@@

\bibitem{Vardy} A. Vardy, "The intractability of computing the minimum distance of a code," in IEEE Transactions on Information Theory, vol. 43, no. 6, pp. 1757-1766, Nov. 1997, doi: 10.1109/18.641542.
